Discon analysis

### 2018-08-02 analysis/01_analysis.Rmd
adding code for data preprocessing

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r data preprocessing}
# Data pre-processing
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(jsonlite)
library(tidyr)
library(stringr)
library(dplyr)
```

```{r data preprocessing}
# Data pre-processing

files <- dir("sandbox-results")

raw_data <- data_frame()
for (f in files) {
  jf <- paste("sandbox-results/",f,sep="")
  jd <- fromJSON(paste(readLines(jf), collapse=""))
  id <- as_data_frame(jd$answers$data$data) %>%
    mutate(workerid = jd$WorkerId)
  raw_data <- bind_rows(raw_data, id)
}

raw_data
```
